Verifying Demonstrations

### 2017-11-20 contents-poster.tex
Adapts to automatic scaling of tikz, changes to A0 paper

  \begin{column}{0.32\linewidth}
    \begin{figure}
      \centering
      \begin{tikzpicture}[%
        -Latex,
        item/.style={rectangle,draw},
        edge from parent/.style={},
        ]
        \tikzset{%
          %grow'=left,%
          %level distance=5em%
        }
        \node[item] (proof) {Proof share}
        child {%
          node[item] (pid) {$pid$}
          child {%
            node[item] (cid) {$cid$}
            child {%
              node[item] (manifesto) {Manifesto}
            }
          }
        }
        child {%
          node[item] (wid) {$wid$}
        }
        child {%
          node[item] (ts) {$t_s$}
        }
        child {%
          node[item] (l) {$l$}
        }
        child {%
          node[item] (wsig) {$wsig$}
        }
        ;

        \path[every node/.style={font=\small}]
        (pid) edge node [anchor=south east] {$\in$} (proof)
        (wid) edge node [anchor=east] {$\in$} (proof)
        (ts) edge node [anchor=east] {$\in$} (proof)
        (l) edge node [anchor=west] {$\in$} (proof)
        (wsig) edge node [anchor=south west] {$\in$} (proof)
        ;

        \path[every node/.style={font=\small}]
        (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
        (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
        (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
        % wsig
        (l) edge[bend right] (wsig)
        (ts) edge[bend right] (wsig)
        (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
          \cdot)$} (wsig)
        ;

      \end{tikzpicture}
      \caption{%
        Structure of a proof share.
        The protester \(P\)'s identifier \(pid\) is computed using the protester's 
        key \(k_P\).
        The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
        \(k_W\).
        \(t_s\) is a time interval and \(l\) is the coordinates of an area.
        The protest (cause) identifier \(cid\) is the hash value of the manifesto.
      }%
      \label{ProofShare}
    \end{figure}%

@@

\flushright
Special thanks to xkcd.com which, over many years, has inspired the stylistic 
presentation of this poster.

>>>>

  \begin{column}{0.32\linewidth}
    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{fig/proofshare.tikz}
      \caption{%
        Structure of a proof share.
        The protester \(P\)'s identifier \(pid\) is computed using the protester's 
        key \(k_P\).
        The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
        \(k_W\).
        \(t_s\) is a time interval and \(l\) is the coordinates of an area.
        The protest (cause) identifier \(cid\) is the hash value of the manifesto.
      }%
      \label{ProofShare}
    \end{figure}%

@@

\vfill
\flushright{}
Special thanks to xkcd.com which, over many years, has inspired the stylistic 
presentation of this poster.
